\documentclass[a4paper,man,natbib,floatsintext,12pt]{apa7}

\usepackage[english]{babel} %character and hyphenation rules specific to the language you choose
%\usepackage[utf8x]{inputenc}
\usepackage{graphicx}
\usepackage{color}
\usepackage{tikz}
\usepackage{amsmath}
\usepackage{blindtext}
\usepackage{tabularx} %great for APA-style Tables
\usepackage{siunitx} % Required for good table ali gnmen
\usepackage{threeparttable}

\sisetup{
  round-mode          = places, % Rounds numbers
  round-precision     = 2, % to 2 places
}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{wrapfig}
\usetikzlibrary{shapes,decorations,arrows,calc,arrows.meta,fit,positioning}
\tikzset{
    -Latex,auto,node distance =1 cm and 1 cm,semithick,
    latent/.style ={ellipse, draw, minimum width = 0.7 cm},
    observed/.style ={rectangle, draw},
    bidirected/.style={Latex-Latex,dashed},
    el/.style = {inner sep=2pt, align=left, sloped}
}
\newcommand{\sigFtest}[4]{\textit{F}(#1,#2) = #3, \textit{p}$<$#4}
\newcommand{\nonsigFtest}[3]{\textit{F}(#1,#2) = #3, \textit{p}$>$.05}


\title{ Laugh with family or strangers? Explore the role of social connectedness in the perception of laughter contagion  }
\shorttitle{Laughter Contagion}
\author{Sarah Liu}
\authorsaffiliations{College of William \& Mary}
\journal{Laughter Journal}

\abstract{Laughter is a universal non-verbal expression of positive emotions in social interaction. It is highly contagious and strongly mediated by the social bonds between listeners and laughers (individuals producing laughter). The primary aim of the current study is to explore the socio-emotional mechanism of contagious laughter, specifically how social connectedness predicts laughter perception. A group of acquainted participants listened to each others’ laughter recordings and rated both the laughter contagiousness and their social connectedness with each laugher. Results indicated that social connectedness positively predicted laughter contagion. Additionally, being informed of the laughter’s identity enhanced contagion rating, suggesting the sense of familiarity significantly boots the perceived contagion in laughter. Notably, people perceive their own laughter as more contagious, which together suggests a social asymmetry in emotion transfer. We further explored two aspects of individual differences in laughter contagion: (1) participants with higher social anxiety experienced contagious laughter to a similar extent as those with lower social anxiety, and (2) scores from the Laughter Production and Perception Questionnaire (LPPQ) — including laughter Frequency, Liking towards laughter, and Usage of laughter — were positively correlated with contagion ratings, supporting LPPQ’s potential as a novel tool for systematically examining everyday laughing behavior.}
\keywords{Laughter contagion, Social Cognition, Social Anxiety}
\authornote{Thanks for my cat helping me write this paper}

\leftheader{Alternate page header in man mode}

%-------------- END PREAMBLE  -------------------


\begin{document}

\maketitle  %Insert my APA style title page

\input{introduction}
\input{method.tex}
\input{Result}
\input{discussion}
\bibliography{reference}



\end{document}